Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-08-15 tex/MesnardoBarba2019.tex
Add DOI for workflow diagram

\begin{figure*}[t]
    \centering
    \includegraphics[width=16cm]{figures/cloud_workflow.png}
    \caption{Reproducible workflow on the public cloud provider Microsoft Azure. Our CFD software is version-controlled with Git and GitHub. We push to DockerHub a Docker image of our CFD application with all its dependencies. Azure CLI is use to configure accounts on Microsoft Azure and to upload/download data to/from an Azure Storage account. With Batch Shipyard, we create a pool on Azure Batch and run container-based simulation using our Docker image.}
    \label{fig:cloud_workflow}
\end{figure*}

>>>>

\begin{figure*}[t]
    \centering
    \includegraphics[width=16cm]{figures/cloud_workflow.png}
    \caption{Reproducible workflow on the public cloud provider Microsoft Azure. Our CFD software is version-controlled with Git and GitHub. We push to DockerHub a Docker image of our CFD application with all its dependencies. Azure CLI is use to configure accounts on Microsoft Azure and to upload/download data to/from an Azure Storage account. With Batch Shipyard, we create a pool on Azure Batch and run container-based simulation using our Docker image. Figure available under CC BY 4.0 license (DOI: https://doi.org/10.6084/m9.figshare.9636722.v1).}
    \label{fig:cloud_workflow}
\end{figure*}
